Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-03 paper/ms.tex
Update intro to schmaction section

In this work, we assume both that an axisymmetric model of the Galaxy is a
good description of the potential and that we have correctly determined the
parameters of that model. We are only concerned with an inaccuracy

>>>>

In this work, we assume both that an axisymmetric model of the Galaxy is a
good description of the potential and that we have correctly determined the
parameters of that model. We are only concerned with an inaccuracy in the
Galactocentric coordinate system and, in particular, the measurement of the
Galactic midplane. Here we determine how an error in either the Galactic
midplane or Galactocentric radius propagates into an error in the various
actions.
